Formal verification of train route planning

### 2025-06-26 paper/main.tex
Explicit contributions

\paragraph{Contributions.}

@@

\subsection{Notations}

>>>>

\paragraph{Contributions.}
Our main contributions are:
\begin{itemize}
	\item Building a formal model of train network. Contrary to most existing works, our model makes very few assumptions: tracks are not directed, we do not distinguish between tracks and stations (platforms are regular tracks).
	\item Writing the TLA+ specification of our model. This specification allows to model check routings.
	\item Defining a composition operator, allowing to build up large routes from smaller part. We use TLA+ to model check resulting composed routes.
\end{itemize}

@@

\paragraph{Notations.}
